---
title: "GDAT622_Week1_HW_James"
author: "James Stanfield"
date: "5/16/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

{
  c("alphahull",     # To calculate the convex hull
    "ca",            # Correspondence analysis
    "conflicted",    # To deal with conflicting function names
    # I've had some strangeness with this
    #  script. I suspect package:conflicted,
    #  but I don't yet know for sure.
    "data.table",    # Fast data input/output
    "dplyr",         # This is all of tidyverse that gets used here
    "dtplyr",        # dplyr syntax with a data.table backend
    "here",          # To find/store files w/o setwd() and getwd()
    "igraph",        # Basic network tools; we'll use statnet mostly
    "igraphdata",    # Some useful datasets
    "intergraph",    # Translate between igraph and statnet formats
    "lmPerm",        # To do permutation tests
    "statnet"      # A suite of network tools, including ERGM and more
  ) -> package_names
  
  for (package_name in package_names) {
    if (!is.element(package_name, installed.packages()[, 1])) {
      install.packages(package_name,
                       repos = "http://cran.mtu.edu/")
      # An alternate, just in case.
      #                      repos="http://lib.stat.cmu.edu/R/CRAN")
    }
    library(
      package_name,
      character.only = TRUE,
      quietly = TRUE,
      verbose = FALSE
    )
  }
  rm(list = c("package_name", "package_names"))
}

set_here()

# Because I like these options:
options(show.signif.stars = FALSE)
options(digits = 4)

```

## Problem 1

Determine whether each of these ties is directed or undirected

International trade - Directed, goods and money transfer in directed transactions

Financial transactions among banks - Directed, similar to above
Preschool children’s stated play preferences - Directed, each child directs to there favorite

College student attendance at university functions - Undirected, equal participants

Who one trusts in an organization - Directed, trust may only flow one way

Advice-seeking among scientific research team members - Directed, similar to trust above

Who one talks to about important matters - Directed, same as previous two

Money lending in a rural Indian community - Directed, Lender to Lendee

Conflict among ethnic groups in South Sudan - Undirected, mutual partners in conflict

Enjoys working with small project teams - Directed, seeks small project teams

Would want to work with future projects with others in a high-tech firm - Directed, seeks high tech firms

Sexual relationships among IV drug users - Undirected, Mutual members of relationship

Lab proximity of scientists in a research institute - Undirected, proximity not directed at other scientists

Observed interactions at a company picnic - Undirected, mutual members of interactions

County commissioners and their votes on policy issues - Undirected, Commissioners do not direct votes at other commissioners

## Problem 2

```{r Problem 2}
#matrix{base} to create a matrix, manually entered values, nrow = number of rows, dimnames = row/column names
prob2 <- matrix(c(0,1,0,0,0,0,0, 1,0,1,0,1,0,0, 0,1,0,1,1,0,0, 0,0,1,0,0,0,0, 0,1,1,0,0,1,0, 0,0,0,0,1,0,1, 0,0,0,0,0,1,0), nrow = 7,
               dimnames = list(c("A","B","C", "D", "E", "F", "G"), c("A","B","C", "D", "E", "F", "G")))
prob2
```


## Problem 3

 Paths: a-b-e-c-d, a-b-e-f-g, d-c-e-f-g
Trails: a-b-e-c-b, f-e-b-c-e, d-c-b-e-c
 Walks: c-e-f-e-c, a-b-e-c-b-a, f-e-b-c-e-f

## Problem 4

```{r Problem 4}
#matrix{base} to create a matrix, manually entered values, nrow = number of rows, dimnames = row/column names
prob4 <- matrix(c(0,8,6,0, 9,0,0,4, 7,5,0,0, 0,3,6,0), nrow = 4,
               dimnames = list(c("JOHN", "JULIA", "JOE", "SALLY"), c("JOHN", "JULIA", "JOE", "SALLY")))
prob4
```


## Problem 5

4 Components: 2 large ones, and 2 isolated nodes

The distance between W9 and W3 is now infinite, as there is no path connecting them

## Problem 6

International trade;
  1 mode, nations v nations

Financial transactions among banks:
  1 mode, banks v banks

Preschool children’s stated play preferences:
  2 mode, children v preferences

College student attendance at university functions:
  2 mode, students v functions

Who one trusts in an organization:
  1 mode, members v members

Advice-seeking among scientific research team members:
  1 mode, members v members

Who one talks to about important matters:
  1 mode, members v members

Money lending in a rural Indian community:
  1 mode, members v members

Conflict among ethnic groups in South Sudan:
  1 mode, groups v groups

Enjoys working with small project teams:
  1 mode, persons v persons

Would want to work with future projects with others in a high-tech firm:
  1 mode, persons v persons

Sexual relationships among IV drug users:
  2 mode, users v users

Lab proximity of scientists in a research institute:
  1 mode, scientists v scientists

Observed interactions at a company picnic:
  1 mode, persons v persons

County commissioners and their votes on policy issues:
  2 mode, commissioners v votes

## Problem 7

```{r Problem 7}
#matrix{base} to create a matrix, manually entered values, nrow = number of rows, dimnames = row/column names
frnd_of_boss <- matrix(c(0,0,1,0, 0,1,0,0, 1,1,0,0, 0,0,0,0), nrow = 4,
               dimnames = list(c("A","B","C", "D"), c("A","B","C", "D")))

frnd_of_boss
```

## Problem 8

 Path: 6-10-2-1-4
Trail: 10-1-7-2-10-5
 Walk: 10-2-1-7-2-10-5
 
## Problem 9

### a

```{r Problem 9 a}

network.initialize(n = 5,                       # network.initialize{network} to create a network object
                   directed = FALSE) -> F2.1
LETTERS[1:5] -> network.vertex.names(F2.1)
network::add.edges(F2.1,                        # add.edges to add the relationships
                   #          
                   tail = c(1, 2, 3, 4, 5),     # "draw" from tail to head, i.e tail(1), head(2), is an edge from 1->2
                   head = c(2, 3, 4, 5, 1))


set.seed(42)
plot.network(F2.1,
             label = network.vertex.names(F2.1),
             arrowhead.cex = 2,
             edge.lwd = 2,
             vertex.col = 8,
             vertex.cex = 3,
             vertex.border = 0)
```

Each node is pivotal for two others, because each is the shortest route between its two neighbors.

### b

```{r Problem 9 b}

network.initialize(n = 8,
                   directed = FALSE) -> F2.1
LETTERS[1:8] -> network.vertex.names(F2.1)
network::add.edges(F2.1,
                   #
                   tail = c(1, 2, 3, 4, 5, 6, 7, 8),
                   head = c(2, 3, 4, 5, 6, 7, 8, 1))


set.seed(42)
plot.network(F2.1,
             label = network.vertex.names(F2.1),
             arrowhead.cex = 2,
             edge.lwd = 2,
             vertex.col = 8,
             vertex.cex = 3,
             vertex.border = 0)
```

Each node is the shortest route between two pairs of two other nodes, for example, E is the fastest way for C or D to reach F or G

### c

```{r Problem 9 c}

network.initialize(n = 4,
                   directed = FALSE) -> F2.1
LETTERS[1:4] -> network.vertex.names(F2.1)
network::add.edges(F2.1,
                   #          
                   tail = c(1,2,3 ),
                   head = c(4,4,4 ))


set.seed(42)
plot.network(F2.1,
             label = network.vertex.names(F2.1),
             arrowhead.cex = 2,
             edge.lwd = 2,
             vertex.col = 8,
             vertex.cex = 3,
             vertex.border = 0)
```

D is pivotal to every other pair of nodes, as it is the only (and therefore shortest) path between every other pair of nodes.

# Problem 10

## a

```{r Problem 10 a}
network.initialize(n = 5,
                   directed = FALSE) -> F2.1
LETTERS[1:5] -> network.vertex.names(F2.1)
network::add.edges(F2.1,
                   #          
                   tail = c(1,2,3,4),
                   head = c(2,3,4,5))

set.seed(42)
plot.network(F2.1,
             label = network.vertex.names(F2.1),
             arrowhead.cex = 2,
             edge.lwd = 2,
             vertex.col = 8,
             vertex.cex = 3,
             vertex.border = 0)
```

B, C, and D are all gatekeepers as removing any of them would separate the network into two components.

## b

```{r Problem 10 b}

network.initialize(n = 5,
                   directed = FALSE) -> F2.1
LETTERS[1:5] -> network.vertex.names(F2.1)
network::add.edges(F2.1,
                   #          
                   tail = c(1, 2, 3, 4, 5),
                   head = c(2, 3, 4, 5, 1))


set.seed(42)
plot.network(F2.1,
             label = network.vertex.names(F2.1),
             arrowhead.cex = 2,
             edge.lwd = 2,
             vertex.col = 8,
             vertex.cex = 3,
             vertex.border = 0)
```

Every node connects two other unconnected nodes, but none are the exclusive path between two nodes.


