---
title: "GDAT622_Invest5_James"
author: "James Stanfield"
date: "6/26/2020"
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

{
  c("alphahull",     # To calculate the convex hull
    "ca",            # Correspondence analysis
    "conflicted",    # To deal with conflicting function names
    # I've had some strangeness with this
    #  script. I suspect package:conflicted,
    #  but I don't yet know for sure.
    "data.table",    # Fast data input/output
    "dplyr",         # This is all of tidyverse that gets used here
    "dtplyr",        # dplyr syntax with a data.table backend
    "here",          # To find/store files w/o setwd() and getwd()
    "igraph",        # Basic network tools; we'll use statnet mostly
    "igraphdata",    # Some useful datasets
    "intergraph",    # Translate between igraph and statnet formats
    "lmPerm",        # To do permutation tests
    "statnet",       # A suite of network tools, including ERGM and more
    "openxlsx",
    "networkdata",
    "farver"         # ggraph and graphlayouts
  ) -> package_names
  
  for (package_name in package_names) {
    if (!is.element(package_name, installed.packages()[, 1])) {
      install.packages(package_name,
                       repos = "http://cran.mtu.edu/")
      # An alternate, just in case.
      #                      repos="http://lib.stat.cmu.edu/R/CRAN")
    }
    library(
      package_name,
      character.only = TRUE,
      quietly = TRUE,
      verbose = FALSE
    )
  }
  rm(list = c("package_name", "package_names"))
}

library(ggraph)
library(graphlayouts)

set_here()

# Because I like these options:
options(show.signif.stars = FALSE)
options(digits = 4)
```

```{r Load data}
fread("Amazon_data/amazon-2003-03-02.txt") -> amazon_el
head(amazon_el)
```

We need to clean up the ID = 0 entries, as Igraph does not like vertices with a name of 0.

```{r modify node names}
# paste an "a" in front of every name
paste0("a", amazon_el$V1) -> amazon_el$V1
paste0("a", amazon_el$`FromNodeId ToNodeId`) -> amazon_el$`FromNodeId ToNodeId`
head(amazon_el)
```

Hopefully we won't have any issues from the node names!

```{r Create Igraph version}
#I'm treating it as undirected, as some methods only work with undirected
graph_from_data_frame(amazon_el, directed = FALSE) -> amazon_igraph
amazon_igraph
```

Now for the long haul, Let's plot the network

```{r Plot the whole thing. }
#start_time <- Sys.time()

#plot(amazon_igraph)

#end_time <- Sys.time()

#end_time - start_time
```

After 3 hours, I wasn't sure if my computer was hung up or if it really needed that long. I stopped the attempt to show the whole network in favor of pursuing other approaches to study the data.

```{r Lovain}
cluster_louvain(amazon_igraph, weights = NULL) -> amazon_louvain
amazon_louvain
```

Louvain identified 210 groups.

```{r Lovain group 1}
amazon_louvain[1]
```


Let's try to only show the first group Louvain pulled out.

```{r Manually force just group 1 network, eval=FALSE, include=FALSE}
dplyr::filter(amazon_el, V1 == c(
    "a0"  ,  "a1"   , "a2"  ,  "a3"  ,  "a4"   , "a5"   , "a6"   , "a10"  , "a12"  ,"a16"  , "a19"  , "a30"  , "a48"  
  ,"a49"  , "a50"   ,"a63"  , "a64"  , "a65"   ,"a66"   ,"a67"   ,"a73"   ,"a74"   ,"a75"  , "a89"  , "a90"  , "a97"  
  ,"a98"  , "a99"   ,"a100" , "a101" , "a108"  ,"a109"  ,"a110"  ,"a116"  ,"a117"  ,"a118" , "a119" , "a123" , "a124" 
  ,"a125" , "a126"  ,"a127" , "a131" , "a135"  ,"a136"  ,"a139"  ,"a149"  ,"a150"  ,"a156" , "a157" , "a158" , "a172" 
  ,"a173" , "a175"  ,"a176" , "a177" , "a180"  ,"a184"  ,"a185"  ,"a186"  ,"a196"  ,"a204" , "a205" , "a206" , "a207" 
  ,"a211" , "a218"  ,"a233" , "a234" , "a246"  ,"a247"  ,"a248"  ,"a257"  ,"a258"  ,"a260" , "a261" , "a262" , "a263" 
  ,"a264" , "a279"  ,"a280" , "a281" , "a282"  ,"a294"  ,"a298"  ,"a307"  ,"a308"  ,"a316" , "a318" , "a320" , "a344" 
  ,"a345" , "a346"  ,"a359" , "a360" , "a361"  ,"a362"  ,"a366"  ,"a367"  ,"a368"  ,"a369" , "a370" , "a372" , "a388" 
  ,"a389" , "a393"  ,"a394" , "a395" , "a396"  ,"a397"  ,"a398"  ,"a400"  ,"a405"  ,"a406" , "a407" , "a411" , "a412" 
  ,"a413" , "a414"  ,"a415" , "a416" , "a417"  ,"a418"  ,"a419"  ,"a430"  ,"a431"  ,"a440" , "a453" , "a460" , "a461" 
  ,"a462" , "a463"  ,"a464" , "a465" , "a466"  ,"a482"  ,"a491"  ,"a492"  ,"a495"  ,"a496" , "a497" , "a498" , "a499" 
  ,"a526" , "a527"  ,"a528" , "a529" , "a530"  ,"a534"  ,"a535"  ,"a536"  ,"a542"  ,"a543" , "a544" , "a547" , "a548" 
  ,"a549" , "a550"  ,"a551" , "a552" , "a553"  ,"a554"  ,"a567"  ,"a569"  ,"a570"  ,"a579" , "a580" , "a584" , "a585" 
  ,"a588" , "a589"  ,"a590" , "a591" , "a594"  ,"a597"  ,"a608"  ,"a609"  ,"a612"  ,"a615" , "a629" , "a630" , "a639" 
  ,"a640" , "a641"  ,"a642" , "a643" , "a644"  ,"a652"  ,"a661"  ,"a662"  ,"a665"  ,"a666" , "a668" , "a669" , "a670" 
  ,"a671" , "a672"  ,"a673" , "a674" , "a675"  ,"a677"  ,"a734"  ,"a735"  ,"a736"  ,"a737" , "a738" , "a739" , "a740" 
  ,"a741" , "a742"  ,"a743" , "a744" , "a745"  ,"a746"  ,"a747"  ,"a748"  ,"a751"  ,"a752" , "a762" , "a769" , "a770" 
  ,"a771" , "a779"  ,"a799" , "a800" , "a801"  ,"a807"  ,"a808"  ,"a827"  ,"a836"  ,"a837" , "a840" , "a841" , "a855" 
  ,"a856" , "a857"  ,"a858" , "a859" , "a867"  ,"a868"  ,"a869"  ,"a870"  ,"a871"  ,"a872" , "a905" , "a906" , "a907" 
  ,"a908" , "a909"  ,"a910" , "a911" , "a912"  ,"a913"  ,"a914"  ,"a918"  ,"a944"  ,"a945" , "a946" , "a947" , "a951" 
  ,"a971" , "a999"  ,"a1000", "a1001", "a1002" ,"a1003" ,"a1004" ,"a1005" ,"a1006" ,"a1034", "a1035", "a1036", "a1037"
  ,"a1038", "a1042" ,"a1043", "a1053", "a1066" ,"a1079" ,"a1080" ,"a1081" ,"a1123" ,"a1124", "a1126", "a1127", "a1128"
  ,"a1132", "a1136" ,"a1137", "a1138", "a1159" ,"a1160" ,"a1167" ,"a1169" ,"a1170" ,"a1175", "a1176", "a1179", "a1187"
  ,"a1188", "a1190" ,"a1196", "a1197", "a1198" ,"a1208" ,"a1209" ,"a1210" ,"a1211" ,"a1212", "a1214", "a1215", "a1216"
  ,"a1217", "a1225" ,"a1226" , "a1227", "a1228" ,"a1229" ,"a1236" ,"a1237" ,"a1242" ,"a1243", "a1244", "a1245", "a1246"
  ,"a1247", "a1256" ,"a1257", "a1259", "a1260" ,"a1271" ,"a1272" ,"a1273" ,"a1274" ,"a1275", "a1314", "a1315", "a1328"
  ,"a1329", "a1330" ,"a1332", "a1344", "a1345" ,"a1346" ,"a1357" ,"a1358" ,"a1359" ,"a1360", "a1362", "a1363", "a1420"
  ,"a1421", "a1457" ,"a1458", "a1472", "a1473" ,"a1474" ,"a1478" ,"a1479" ,"a1492" ,"a1493", "a1494", "a1496", "a1505"
  ,"a1506", "a1507" ,"a1510", "a1511", "a1512" ,"a1521" ,"a1522" ,"a1527" ,"a1551" ,"a1552", "a1554", "a1555", "a1556"
  ,"a1669", "a1670" ,"a1680", "a1681", "a1700" ,"a1701" ,"a1712" ,"a1715" ,"a1716" ,"a1717", "a1722", "a1723", "a1724"
  ,"a1729", "a1730" ,"a1740", "a1741", "a1753" ,"a1754" ,"a1755" ,"a1756" ,"a1757" ,"a1778", "a1779", "a1780", "a1781"
  ,"a1803", "a1806" ,"a1807", "a1858", "a1859" ,"a1860" ,"a1861" ,"a1863" ,"a1887" ,"a1888", "a1889", "a1892", "a1893"
  ,"a1922", "a1923" ,"a1924", "a1948", "a1949" ,"a1952" ,"a1953" ,"a1959" ,"a1960" ,"a1961", "a1965", "a1966", "a1967"
  ,"a2004", "a2005" ,"a2006", "a2007", "a2019" ,"a2020" ,"a2021" ,"a2029" ,"a2031" ,"a2041", "a2042", "a2043", "a2054"
  ,"a2055", "a2090" ,"a2091", "a2092", "a2101" ,"a2102" ,"a2118" ,"a2134" ,"a2135" ,"a2136", "a2137", "a2138", "a2139"
  ,"a2140", "a2141" ,"a2142", "a2149", "a2150" ,"a2151" ,"a2152" ,"a2162" ,"a2163" ,"a2164", "a2165", "a2166", "a2167"
  ,"a2168", "a2193" ,"a2194", "a2195", "a2196" ,"a2233" ,"a2234" ,"a2235" ,"a2236" ,"a2237", "a2238", "a2239", "a2240"
  ,"a2241", "a2242" ,"a2251", "a2252", "a2253" ,"a2301" ,"a2302" ,"a2303" ,"a2304" ,"a2305", "a2311", "a2312", "a2313"
  ,"a2393", "a2403" ,"a2404", "a2405", "a2406" ,"a2407" ,"a2431" ,"a2432" ,"a2460" ,"a2462", "a2464", "a2465", "a2466"
  ,"a2467", "a2468" ,"a2469", "a2484", "a2486" ,"a2487" ,"a2559" ,"a2568" ,"a2569" ,"a2578", "a2596", "a2597", "a2598"
  ,"a2601", "a2602" ,"a2610", "a2611", "a2612" ,"a2613" ,"a2614" ,"a2615" ,"a2656" ,"a2711", "a2712", "a2713", "a2715"
  ,"a2716", "a2722" ,"a2723", "a2725", "a2726" ,"a2727" ,"a2728" ,"a2729" ,"a2730" ,"a2731", "a2732", "a2735", "a2736"
  ,"a2737", "a2738" ,"a2742", "a2746", "a2753" ,"a2754" ,"a2755" ,"a2756" ,"a2757" ,"a2758", "a2772", "a2778", "a2779"
  ,"a2780", "a2781" ,"a2790", "a2791", "a2847" ,"a2848" ,"a2854" ,"a2855" ,"a2872" ,"a2873", "a2885", "a2909", "a2945"
  ,"a2946", "a2947" ,"a2958", "a2960", "a2961" ,"a2962" ,"a2963" ,"a2964" ,"a2965" ,"a2970", "a2972", "a2973", "a2974"
  ,"a2975", "a2976" ,"a2977", "a3023", "a3024" ,"a3027" ,"a3043" ,"a3044" ,"a3045" ,"a3121", "a3122", "a3147", "a3176"
  ,"a3177", "a3178" ,"a3183", "a3184", "a3185" ,"a3186" ,"a3207" ,"a3208" ,"a3209" ,"a3210", "a3224", "a3225", "a3226"
  ,"a3227", "a3238" ,"a3239", "a3240", "a3261" ,"a3262" ,"a3263" ,"a3264" ,"a3265" ,"a3274", "a3275", "a3276", "a3308"
  ,"a3332", "a3333" ,"a3358", "a3359", "a3360" ,"a3363" ,"a3364" ,"a3365" ,"a3366" ,"a3367", "a3373", "a3374", "a3375"
  ,"a3376", "a3377" ,"a3378", "a3409", "a3410" ,"a3411" ,"a3444" ,"a3445" ,"a3453" ,"a3454", "a3455", "a3463", "a3465"
  ,"a3466", "a3475" ,"a3478", "a3479", "a3489" ,"a3495" ,"a3496" ,"a3520" ,"a3526" ,"a3527", "a3528", "a3530", "a3532"
  ,"a3533", "a3539" ,"a3540", "a3541", "a3555" ,"a3576" ,"a3577" ,"a3578" ,"a3579" ,"a3580", "a3581", "a3582", "a3583"
  ,"a3584", "a3597" ,"a3598", "a3599", "a3600" ,"a3601" ,"a3602" ,"a3616" ,"a3617" ,"a3636", "a3637", "a3638", "a3639"
  ,"a3640", "a3641" ,"a3642", "a3643", "a3644" ,"a3648" ,"a3649" ,"a3650" ,"a3651" ,"a3726", "a3727", "a3728", "a3775"
  ,"a3776", "a3777" ,"a3778", "a3779", "a3780" ,"a3781" ,"a3820" ,"a3821" ,"a3822" ,"a3824", "a3825", "a3826", "a3827"
  ,"a3828", "a3842" ,"a3843", "a3846", "a3874" ,"a3875" ,"a3876" ,"a3877" ,"a3878" ,"a3879", "a3884", "a3885", "a3946"
  ,"a3969", "a3970" ,"a3971", "a3991", "a3992" ,"a3993" ,"a3994" ,"a3997" ,"a3998" ,"a3999", "a4000", "a4004", "a4005"
  ,"a4006", "a4007" ,"a4008", "a4034", "a4035" ,"a4036" ,"a4037" ,"a4047" ,"a4056" ,"a4057", "a4058", "a4059", "a4086"
  ,"a4087", "a4098" ,"a4105", "a4106", "a4136" ,"a4157" ,"a4158" ,"a4159" ,"a4190" ,"a4191", "a4192", "a4193", "a4208"
  ,"a4209", "a4210" ,"a4211", "a4246", "a4266" ,"a4267" ,"a4268" ,"a4269" ,"a4282" ,"a4322", "a4323", "a4324", "a4325"
  ,"a4346", "a4347" ,"a4369", "a4370", "a4371" ,"a4379" ,"a4380" ,"a4381" ,"a4386" ,"a4387", "a4388", "a4401", "a4418"
  ,"a4419", "a4455" ,"a4465", "a4480", "a4499" ,"a4500" ,"a4501" ,"a4502" ,"a4510" ,"a4511", "a4535", "a4553", "a4554"
  ,"a4565", "a4566" ,"a4567", "a4568", "a4569" ,"a4570" ,"a4588" ,"a4589" ,"a4603" ,"a4657", "a4658", "a4659", "a4660"
  ,"a4682", "a4683" ,"a4684", "a4685", "a4686" ,"a4687" ,"a4688" ,"a4719" ,"a4720" ,"a4721", "a4722", "a4751", "a4752"
  ,"a4753", "a4754" ,"a4755", "a4756", "a4757" ,"a4786" ,"a4788" ,"a4809" ,"a4810" ,"a4847", "a4850", "a4851", "a4852"
  ,"a4857", "a4858" ,"a4859", "a4860", "a4861" ,"a4922" ,"a4947" ,"a4948" ,"a4949" ,"a4975", "a4976", "a5011", "a5012"
  ,"a5013", "a5014" ,"a5015", "a5016", "a5053" ,"a5054" ,"a5071" ,"a5072" ,"a5073" ,"a5077", "a5078", "a5174", "a5175"
  ,"a5176", "a5204" ,"a5205", "a5206", "a5217" ,"a5270" ,"a5271" ,"a5299" ,"a5300" ,"a5302", "a5319", "a5321", "a5335"
  ,"a5351", "a5370" ,"a5384", "a5385", "a5439" ,"a5440" ,"a5503" ,"a5504" ,"a5531" ,"a5532", "a5533", "a5534", "a5535"
  ,"a5552", "a5553" ,"a5554", "a5560", "a5561" ,"a5562" ,"a5567" ,"a5568" ,"a5569" ,"a5572", "a5573", "a5574", "a5582"
  ,"a5583", "a5584" ,"a5585", "a5586", "a5587" ,"a5603" ,"a5604" ,"a5662" ,"a5663" ,"a5664", "a5665", "a5671", "a5722"
  ,"a5723", "a5724" ,"a5743", "a5744", "a5764" ,"a5766" ,"a5783" ,"a5824" ,"a5830" ,"a5890", "a5891", "a5892", "a5897"
  ,"a5919", "a5920" ,"a5983", "a5985", "a5986" ,"a5998" ,"a6048" ,"a6058" ,"a6059" ,"a6061", "a6062", "a6091", "a6092"
  ,"a6093", "a6102" ,"a6103", "a6139", "a6140" ,"a6141" ,"a6143" ,"a6144" ,"a6145" ,"a6146", "a6160", "a6171", "a6178"
  ,"a6223", "a6224" ,"a6234", "a6239", "a6240" ,"a6263" ,"a6296" ,"a6297" ,"a6298" ,"a6299", "a6300", "a6329", "a6330"
  ,"a6356", "a6403" ,"a6404", "a6405", "a6516" ,"a6523" ,"a6535" ,"a6536" ,"a6542" ,"a6543", "a6544", "a6545", "a6552"
  ,"a6553", "a6569" ,"a6570", "a6577", "a6610" ,"a6611" ,"a6623" ,"a6635" ,"a6637" ,"a6638", "a6690", "a6700"
))
```

```{r For loop to filter out group 1}

#Isolate group 1
amazon_louvain[1] -> al_1
#n_distinct(al_1$`1`) to give us the length of the for loop

#initialize our collection data
temp2 <- character()

#for each member of group 1
for (i in 1:n_distinct(al_1$`1`)) {
  
  #Filter out the V1 values that match
  dplyr::filter(amazon_el, V1 == al_1$`1`[i]) -> temp1
  
  #and combine with all other group 1 edges
  temp2 <- bind_rows(temp2, temp1)
  
}

str(temp2)
```

```{r Plot group 1}
set.seed(42)

#Take our group 1 edgelist and clean out any rows with NAs
amazon_g1 <- na.omit(temp2)

#Convert edgelist to igraph
graph_from_data_frame(amazon_g1, directed = FALSE) -> g1_igraph

#plot without labels, I made the nodes small and unlabeled so we can see the edges better
plot(g1_igraph, vertex.label=NA, vertex.size = .5)

```


Looking at group 1, we can see what mostly appears to be a hairball. However, we can see what appears to be a further breakdown of approximately 4 large groups.

```{r Lovain of g1}
cluster_louvain(g1_igraph) -> g1_lovain
g1_lovain
```


```{r Sub_group 2 edgelist}

#Isolate sub-group 2
g1_lovain[1] -> g1_s1
#n_distinct(al_1$`1`) to give us the length of the for loop

#initialize our collection data
temp2 <- character()

#for each member of group 1
for (i in 1:n_distinct(g1_s1$`1`)) {
  
  #Filter out the V1 values that match
  dplyr::filter(amazon_el, V1 == g1_s1$`1`[i]) -> temp1
  
  #and combine with all other group 1 edges
  temp2 <- bind_rows(temp2, temp1)
  
}

str(temp2)
```

```{r g1_s1 igraph}
#transfer temp2 to new data.frame
temp2 -> g1_s1_el

#create igraph object
graph_from_data_frame(g1_s1_el) -> g1_s1_igraph

g1_s1_igraph
```

```{r}
plot(g1_s1_igraph)
```

```{r}
transitivity(g1_s1_igraph)

g1_s1_igraph$eigen  <- centr_eigen(g1_s1_igraph)
g1_s1_igraph$betw   <- centr_betw(g1_s1_igraph)

plot(g1_s1_igraph, edge.size = 0.5, arrow.size = 0.5,
     vertex.size = g1_s1_igraph$eigen$vector*20)

plot(g1_s1_igraph, edge.size = 0.5, arrow.size = 0.5,
     vertex.size = g1_s1_igraph$betw$res)
```

A transitivity of almost 0.5 shows that there is a definite tendency to fulfill the strong triadic closure property. This is to be expected, as this is relating products that are bought together.

Looking at eigen vs betweeness, The nodes that catch the eye are: a1004 and a1007.

Searching the meta text, we get:

Id:   1004
ASIN: 0531112004
  title: How to Write a Term Paper (A Speak Out, Write on! Book)
  group: Book
  salesrank: 837629
  similar: 0
  categories: 1
   |Books[283155]|Subjects[1000]|Children's Books[4]|Reference & Nonfiction[3176]|Language Arts[3182]|Composition & Creative Writing[3183]
  reviews: total: 1  downloaded: 1  avg rating: 5
    1999-8-22  cutomer:  ATVPDKIKX0DER  rating: 5  votes:  10  helpful:   2
    


Id:   1007
ASIN: 0443071373
  title: Clinical Pharmacy and Therapeutics
  group: Book
  salesrank: 706603
  similar: 0
  categories: 2
   |Books[283155]|Subjects[1000]|Medicine[13996]|Pharmacology[14080]|Pharmacy[14088]
   |Books[283155]|Subjects[1000]|Professional & Technical[173507]|Medical[173514]|Pharmacology[265544]|Pharmacy[265548]
  reviews: total: 0  downloaded: 0  avg rating: 0


Starting with 1007, we can see from the plots that it is surrounded by 1864 - 1868.

Id:   1864
ASIN: 069401057X
  title: Zoom City (Growing Tree)
  group: Book
  salesrank: 66993
  similar: 5  0694010588  0694010723  0694006513  1552090345  0694010391
  categories: 6
   |Books[283155]|Subjects[1000]|Children's Books[4]|Baby-3[2752]|Basic Concepts[2753]|General[2765]
   |Books[283155]|Subjects[1000]|Children's Books[4]|Baby-3[2752]|Board Books[2778]
   |Books[283155]|Subjects[1000]|Children's Books[4]|Authors & Illustrators, A-Z[170540]|( H )[170548]|Hurd, Thacher[170709]
   |[540744]|Specialty Stores[547930]|Books, Music & More[559958]|Books for Babies[692218]|Board Books[692220]
   |[540744]|Specialty Stores[547930]|Books, Music & More[559958]|Books for Babies[692218]|Concept Books[694936]|General[694944]
   |Books[283155]|Subjects[1000]|Children's Books[4]|Baby-3[2752]|General[3049241]
  reviews: total: 11  downloaded: 11  avg rating: 4
    1998-9-30  cutomer:  ATVPDKIKX0DER  rating: 5  votes:   0  helpful:   0
    1998-10-2  cutomer:  ATVPDKIKX0DER  rating: 5  votes:   1  helpful:   1
    1999-7-31  cutomer:  ATVPDKIKX0DER  rating: 5  votes:   2  helpful:   2
    2000-3-24  cutomer: A1RYHBX54KOLWD  rating: 5  votes:   1  helpful:   1
    2000-10-23  cutomer: A3SMR4HRFJARSC  rating: 2  votes:   0  helpful:   0
    2001-4-30  cutomer:  A87BV8TBFB0C5  rating: 5  votes:   4  helpful:   4
    2001-8-2  cutomer:  AM9KJ9C2VLVK8  rating: 2  votes:   5  helpful:   3
    2002-1-8  cutomer: A1OZ8X4ZK4SFFQ  rating: 2  votes:   5  helpful:   1
    2003-6-22  cutomer: A3UOI3KH0BZK58  rating: 5  votes:   0  helpful:   0
    2004-10-5  cutomer:  AOM91Q2SIB4ZN  rating: 5  votes:   0  helpful:   0
    2005-1-6  cutomer: A389VZ934X0K9R  rating: 5  votes:   0  helpful:   0

Id:   1865
ASIN: 0486654605
  title: Catalysis in Chemistry and Enzymology
  group: Book
  salesrank: 116258
  similar: 5  0126437319  0716732688  0471359297  0471303097  0199638209
  categories: 2
   |Books[283155]|Subjects[1000]|Science[75]|Chemistry[13570]|Physical & Theoretical[13588]
   |Books[283155]|Subjects[1000]|Professional & Technical[173507]|Professional Science[173510]|Chemistry[227282]|Physical & Theoretical[227289]
  reviews: total: 1  downloaded: 1  avg rating: 5
    2004-1-4  cutomer: A1DIZO95XRBLPO  rating: 5  votes:   1  helpful:   1

Id:   1866
ASIN: 0765801485
  title: Media and Democracy in Africa
  group: Book
  salesrank: 1726823
  similar: 0
  categories: 6
   |Books[283155]|Subjects[1000]|History[9]|Africa[4762]|General[4776]
   |Books[283155]|Subjects[1000]|Nonfiction[53]|Government[10753]|Democracy[10761]
   |Books[283155]|Subjects[1000]|Law[10777]|Perspectives on Law[173495]|Non-US Legal Systems[10955]
   |Books[283155]|Subjects[1000]|Nonfiction[53]|Social Sciences[11232]|Special Groups[11298]|African-American Studies[11300]
   |Books[283155]|Subjects[1000]|Professional & Technical[173507]|Law[173518]|Perspectives on Law[227505]|Non-US Legal Systems[227513]
   |Books[283155]|Subjects[1000]|Nonfiction[53]|Social Sciences[11232]|Media Studies[13022421]
  reviews: total: 0  downloaded: 0  avg rating: 0

Id:   1867
ASIN: B00007KIBN
  title: Pacific Chants: Polynesian Himene
  group: Music
  salesrank: 53183
  similar: 5  B000093FHF  B000004BQU  B000003EKA  B000003EK1  B00000412X
  categories: 3
   |Music[5174]|Styles[301668]|International[33]|General[63848]
   |Music[5174]|Styles[301668]|New Age[36]|General[63957]
   |Music[5174]|Specialty Stores[468040]|Indie Music[266023]|International[171245]|General[520182]
  reviews: total: 1  downloaded: 1  avg rating: 5
    2004-1-24  cutomer: A1O2IZYNEX8RW2  rating: 5  votes:   5  helpful:   5

Id:   1868
ASIN: 0965669408
  title: 111 Days to Zion
  group: Book
  salesrank: 1200784
  similar: 0
  categories: 0
  reviews: total: 0  downloaded: 0  avg rating: 0

I can see why a book about pharmocology (1007) would be tied to a book on chemistry and enzymology (1865), but I'm unsure why it would end up tied to a children's book (1864), and two social/cultural texts (1866 and 1867). 1868 provides nothing but the title in this data, but a quick google search identifies it as a book about Mormon history.

If I was pressed to make a profile of the person who would buy these items together, I would say a college student who is purchasing text books for both STEM and Liberal Arts courses, and has either a child or a much younger sibling and/or niece/nephew.

Seeing a book on how to write a term paper in the same subgroup is not surprising, as it would fit with our image of a college student.

```{r Blockmodel, eval=FALSE, include=FALSE}
matrix(data = na.omit(g1_s1_el)) -> g1_s1_mat

network(g1_s1_mat, matrix.type == "edgelist", directed = TRUE, bipartite = FALSE) -> g1_s1_net

# Run equivalence cluster
equiv.clust(g1_s1_igraph) %>% plot(.)

#sna::blockmodel creates a blockmodel from  a graph and clutering object, set k = 4 based on equiv.clust results
blockmodel(rdgam_net, equiv.clust(rdgam_net), k = 4) -> rdgam_block
plot(rdgam_block)
```
Error in if (matrix.type == "edgelist") { : missing value where TRUE/FALSE needed

I wanted to do some clustering and a blockmodel, but I couldn't convert the data into a network object, which is needed for those functions to work. I just kept getting the error message above.








