---
title: "GDAT622_week2_HW_James"
author: "James Stanfield"
date: "5/25/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
 
{
  c("alphahull",     # To calculate the convex hull
    "ca",            # Correspondence analysis
    "conflicted",    # To deal with conflicting function names
    # I've had some strangeness with this
    #  script. I suspect package:conflicted,
    #  but I don't yet know for sure.
    "data.table",    # Fast data input/output
    "dplyr",         # This is all of tidyverse that gets used here
    "dtplyr",        # dplyr syntax with a data.table backend
    "here",          # To find/store files w/o setwd() and getwd()
    "igraph",        # Basic network tools; we'll use statnet mostly
    "igraphdata",    # Some useful datasets
    "intergraph",    # Translate between igraph and statnet formats
    "lmPerm",        # To do permutation tests
    "statnet"      # A suite of network tools, including ERGM and more
  ) -> package_names
  
  for (package_name in package_names) {
    if (!is.element(package_name, installed.packages()[, 1])) {
      install.packages(package_name,
                       repos = "http://cran.mtu.edu/")
      # An alternate, just in case.
      #                      repos="http://lib.stat.cmu.edu/R/CRAN")
    }
    library(
      package_name,
      character.only = TRUE,
      quietly = TRUE,
      verbose = FALSE
    )
  }
  rm(list = c("package_name", "package_names"))
}

set_here()

# Because I like these options:
options(show.signif.stars = FALSE)
options(digits = 4)

```

# Function to read in UCINET data

```{r}
read.ucinet.header <- function(filename) {
  # function for reading UCINET header files (recent versions only)
  # This only works for "single level" files. (In spreadsheet parlance, 
  # each workbook can have only one sheet.)
  UCINET.header <- file(paste(filename,".##h",sep=''),"rb")
  ignore <- readBin(UCINET.header,what="int",size=1)
  headerversion <- paste(
    rawToChar(readBin(UCINET.header,what="raw",size=1)),
    rawToChar(readBin(UCINET.header,what="raw",size=1)),
    rawToChar(readBin(UCINET.header,what="raw",size=1)),
    rawToChar(readBin(UCINET.header,what="raw",size=1)),
    rawToChar(readBin(UCINET.header,what="raw",size=1)),
    sep='')
  if (!(headerversion %in% c('DATE:','V6404'))) {
    close(UCINET.header)
    stop(paste('unknown header type; try more recent UCINET file types'))
  }
  year <- 2000+readBin(UCINET.header,what="int",size=2)
  month <- c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug',
             'Sep','Oct','Nov','Dec')[readBin(UCINET.header,what="int",size=2)]
  day <- readBin(UCINET.header,what="int",size=2)
  dow <- c('Monday','Tuesday','Wednesday','Thursday','Friday',
           'Saturday','Sunday')[readBin(UCINET.header,what="int",size=2)]
  labtype <- readBin(UCINET.header,what="int",size=2)
  infile.dt <- c('nodt','bytedt','booleandt','shortintdt','worddt',
                 'smallintdt','longintdt',' singledt','realdt','doubledt',
                 'compdt','extendeddt','labeldt','setdt','stringdt','pointerdt',
                 'chardt','integerdt','nodelistdt','sparsedt','int64dt')[
                   readBin(UCINET.header,what="int",size=1)]
  ndim <- readBin(UCINET.header,what="int",size=2)
  if (headerversion=='V6404') {fct=2} else {fct=1}
  dims <- c(readBin(UCINET.header,what="int",size=2*fct),
            readBin(UCINET.header,what="int",size=2*fct))
  if (ndim==3) {
    dims[3] <- readBin(UCINET.header,what="int",size=2*fct)
  }
  if (!(ndim==2|ndim==3&dims[3]==1)) {
    close(UCINET.header)
    stop(paste('UCINET file with',dims[3],'levels; please convert separately'))
  }
  t.length <- readBin(UCINET.header,what="int",size=1)
  if (t.length>0){
    titl <- sapply(1:t.length, function(i){
      rawToChar(readBin(UCINET.header,what="raw",size=1))
    })
    titl <- paste(titl,collapse='')
  } else {titl <- ''}
  haslab <- c(readBin(UCINET.header,what="logical",size=1),
              readBin(UCINET.header,what="logical",size=1))
  if (ndim==3) {
    haslab[3] <- readBin(UCINET.header,what="logical",size=1)
  }
  dim.labels <- list()
  for (arr.dim in 1:length(dims)) {
    if (haslab[arr.dim]) {
      dim.labels[[arr.dim]] <- rep(NA,dims[arr.dim])
      for (i in 1:dims[arr.dim]) {
        lab <- ''
        lablen <- readBin(UCINET.header,what="int",size=2)
        for (let in 1:lablen) {
          lab <- paste(lab,
                       rawToChar(readBin(UCINET.header,what="raw",size=1)),
                       sep='')
        }
        dim.labels[[arr.dim]][i] <- lab
      }
    }}
  close(UCINET.header)
  if (ndim==3&dims[3]==1) {
    titl <- dim.labels[[3]][1]
    warning(paste('UCINET file with one level; level name "',
                  titl,'" treated as network name',sep=''))
    ndim <- 2
    dims <- dims[1:2]
    haslab <- haslab[1:2]
    dim.labels <- dim.labels[1:2]
  }
  return(list(
    headerversion=headerversion,
    date=paste(dow,paste(day,month,year,sep='-')),
    labtype=labtype,
    infile.dt=infile.dt,
    ndim=ndim,
    dims=dims,
    title=titl,
    haslab=haslab,
    dim.labels=dim.labels
  ))
}

read.ucinet <- function(filename) {
  # function for reading UCINET data files (recent versions only)
  # filename = UCINET filename (without ## extension)
  # begin of main function code:
  header <- read.ucinet.header(filename)
  UCINET.data <- file(paste(filename,".##d",sep=''),"rb")
  thedata <- c()
  for (i in 1:(header$dims[1]*header$dims[2]))
    thedata[i] <- readBin(UCINET.data,what="numeric",size=4,endian='little')
  close(UCINET.data)
  mat <- matrix(thedata,nr=header$dims[2],nc=header$dims[1],
                dimnames=header$dim.labels[c(2,1)],byrow=TRUE)
  # put additional info from header file on matrix
  if (header$title!='') {attr(mat,'title') <- header$title}
  attr(mat,'date') <- header$date
  #attr(mat,'labtype') <- header$labtype
  #attr(mat,'infile.dt') <- header$infile.dt
  return(mat)
}
```

# Problem 1

```{r Prob 1 - Distance Matrix}
#matrix{base} to create a matrix, manually entered values, nrow = number of rows, dimnames = row/column names
prob1_mat <- matrix(c(0,1,2,3,2,3,4, 1,0,1,2,1,2,3, 2,1,0,1,1,2,3, 3,2,1,0,2,3,4, 2,1,1,2,0,1,2, 3,2,2,3,1,0,1, 4,3,3,4,2,1,0), 
                nrow = 7,
                ncol = 7,
                byrow = TRUE)

c("A","B","C", "D", "E", "F", "G") -> prob1_names -> rownames(prob1_mat) -> colnames(prob1_mat)

as.dist(prob1_mat) -> prob1_dist #as.dist to convert to distance type
prob1_dist
```

```{r Prob 1 - MDS}
fit <- cmdscale(prob1_dist, eig = TRUE, k = 2) #cmdscale {stats} performs MultiDimensional Scaling (MDS)
x <- -fit$points[, 1]  # Otherwise, the plot is reversed
y <- fit$points[, 2]   # This should be reversed, but isn't in
#  the text

{
  plot(x, y, pch = 19, xlim = range(x) + c(0, 5))
  text(x, y, pos = 4, labels = prob1_names)
}
```

# Problem 2

```{r Prob 2 - matrix}
prob2_mat <- matrix(c(11,4,7,0, 11,2,14,7, 2,12,11,14, 8,7,9,15, 9,6,6,12), 
                nrow = 5,
                ncol = 4,
                byrow = TRUE,
                dimnames = list(
                  "Ethnic Group" = c("Older Italian", "Younger_Italian", "Lower48-1", "Lower48-2", "Lower48-3"),
                  "Theme" = c("Groups", "Single", "Work", "Aesthetic")))

prob2_mat
```

```{r Prob 2 - Masses}
#sum up all the values in the table
prob2_n = sum(prob2_mat)
#compute the table of proportions, P
prob2_P = prob2_mat / prob2_n

#Calculate the row and column masses
prob2_column.masses = colSums(prob2_P)
prob2_row.masses = rowSums(prob2_P)
prob2_row.masses
prob2_column.masses
```

We can see that Older Italians make up 13.17% of participants, and 28.14% of photos had a work theme.
Assuming that ethnicity has no effect on photo themes, we would expect ~3% of participants
to be Older Italians who took Work themes photos (13.17% of 28.14%).

We can calculate all of these expected values.

```{r Prob 2 - Expected Values}
prob2_E = prob2_row.masses %o% prob2_column.masses
prob2_E
```

```{r Prob 2 - Residuals}
#Calculate residuala
prob2_R = prob2_P - prob2_E

#Convert to indexed residuals
prob2_I = prob2_R / prob2_E
prob2_I
```

Relative to our expectations, Older Italians are twice as likely to take group photos and took no aesthetic images; while Younger Italians favored Work themes pictures.

Lower48-1 took more single person or aesthetic photos, while Lower48-2 only favored the aesthetic, and Lower48-3 went for group and aesthetic.


# Problem 3

```{r Prob 3 - MDS}
# Read Data/Science_Collaboration from the UCI data:
read.ucinet.header(here("Data/Science_Collaboration")) -> prob3_hdr
read.ucinet(here("Data/Science_Collaboration")) -> prob3_mat
prob3_hdr$dim.labels[[1]] -> rownames(prob3_mat) -> colnames(prob3_mat)

#Convert matrix to distance matrix

as.dist(prob3_mat) -> prob3_dist #as.dist to convert to distance type

prob3_fit <- cmdscale(prob3_dist, eig = TRUE, k = 2) #cmdscale {stats} performs MultiDimensional Scaling (MDS)
prob3_x <- -prob3_fit$points[, 1]  # Otherwise, the plot is reversed
prob3_y <- prob3_fit$points[, 2]   # This should be reversed, but isn't in
#  the text

{
  plot(prob3_x, prob3_y, pch = 19, xlim = range(prob3_x) + c(0, 5), ylim = range(prob3_y))
  text(prob3_x, prob3_y, pos = 4, labels = prob3_hdr$dim.labels[[1]])
}
```

It looks like there is an extremely high degree of collaboration. Of the the 42 members, 37 appear to be pretty much on top of each other.

```{r Prob 3 - Stress}
#put code for calculating stress here
```

# Problem 4

```{r Prob 4 -  Hierarchical Clustering}
#Using same distance matrix from problem 3
prob4_dist <- prob3_dist

# cluster using hclust {stats}
hclust(prob4_dist, method="average") -> prob4_hc_ave
# plot the dendrogram
plot(prob4_hc_ave)
prob4_hc_ave$height
```

We can see the groups separating pretty early. At the bottom, we have 2 main groups which each hold roughly a third each, while the remaining third is divided into four other groups (one of which holds only a single member).



# Problem 5
























