---
title: "GDAT622_Invest_2"
author: "James Stanfield"
date: "6/6/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

{
  c("alphahull",     # To calculate the convex hull
    "ca",            # Correspondence analysis
    "conflicted",    # To deal with conflicting function names
    # I've had some strangeness with this
    #  script. I suspect package:conflicted,
    #  but I don't yet know for sure.
    "data.table",    # Fast data input/output
    "dplyr",         # This is all of tidyverse that gets used here
    "dtplyr",        # dplyr syntax with a data.table backend
    "here",          # To find/store files w/o setwd() and getwd()
    "igraph",        # Basic network tools; we'll use statnet mostly
    "igraphdata",    # Some useful datasets
    "intergraph",    # Translate between igraph and statnet formats
    "lmPerm",        # To do permutation tests
    "statnet",       # A suite of network tools, including ERGM and more
    "openxlsx",
    "networkdata",
    "R.matlab",
    "farver"         # ggraph and graphlayouts
  ) -> package_names
  
  for (package_name in package_names) {
    if (!is.element(package_name, installed.packages()[, 1])) {
      install.packages(package_name,
                       repos = "http://cran.mtu.edu/")
      # An alternate, just in case.
      #                      repos="http://lib.stat.cmu.edu/R/CRAN")
    }
    library(
      package_name,
      character.only = TRUE,
      quietly = TRUE,
      verbose = FALSE
    )
  }
  rm(list = c("package_name", "package_names"))
}

library(ggraph)
library(graphlayouts)

set_here()

# Because I like these options:
options(show.signif.stars = FALSE)
options(digits = 4)
```

```{r Load data and pull out matrix}
readMat(here("Data/facebook100/Howard90.mat")) -> how_data
how_data$A -> how_mat
```

```{r edges}
ergm(how_mat ~ edges) -> how1         # AIC: 3831040
summary(how1)
```

So starting with edges gives us an AIC of 3831040 to start

```{r istar}
ergm(how_mat ~ edges + istar(2)) -> how2  # AIC: 3824915
summary(how2)
```

AIC dropped.

```{r mutual}

ergm(how_mat ~ edges + istar(2) + mutual) -> how3  # AIC: 3658574
summary(how3)
```

That's another AIC drop.

After the last ergm took so long to run, I'm not inclined to add any other predictors.
Looking at what we have, both number of ties (edges) and repriprocity of ties (mutual)
were considered significant in how2 model. Unfortunately, the p-value of mutual is
given as NA above. Lets's look at the values for our predictors.

The istar values is incredibly small compared to edges and mutual, so we can probably ignore that term with very little trouble.

The mutual term is the largest as well as positive, meaning that the model predicts that connections are very likely to be returned.

Let's do some more diagnostics.

```{r mcmc diagnostics}
mcmc.diagnostics(how3)
```

well diagnostics pretty much just says that it can't compute properly, so I won't be accepting anything from the output as accurate.



































